Beta to Release Matching: Proof-of-Concept

### 2019-10-01 poc/report_poc.Rmd
Moving reports over

---
title: "Beta to Release Matching"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

* Browser engagement
    - uri_count
    - search_count
    - active_hours
    - num_pages
    - daily_max_tabs
    - daily_unique_domains
    - daily_num_sessions_started
    - daily_tabs_opened
* Frequency of Browser Usage
    - num_active_days
    - daily_num_sessions_started
    - session_length
    - profile_age
* Environment
    - cpu_cores
    - cpu_speed_mhz
    - memory_mb
    - os
    - os_version
    - is_wow64
    - distribution_id
* Geo
    - country
    - timezone_offset
* Settings
    - num_bookmarks
    - num_addons
    - sync_configured
    - is_default_browser

>>>>

---
title: "Beta to Release Matching: Proof-of-Concept"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

* Browser engagement
    - uri_count
    - search_count
    - active_hours
    - num_pages
    - daily_max_tabs
    - daily_unique_domains
    - daily_tabs_opened
* Frequency of Browser Usage
    - num_active_days
    - daily_num_sessions_started
    - session_length
    - profile_age
* Environment
    - cpu_cores
    - cpu_speed_mhz
    - memory_mb
    - os
    - os_version
    - is_wow64
    - distribution_id
* Geo
    - country
    - timezone_offset
* Settings
    - num_bookmarks
    - num_addons
    - sync_configured
    - is_default_browser
